Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-02-28 additional_files/main_text.tex
Remove vg results from Table 1

			\csvreader[head to column names,
			tabular = llllcccc,
			table head = \toprule Trait & Locus & Gene & Causal variant & Platypus\tnote{a} & vg\tnote{b} & Paragraph\tnote{b} & \textit{k}-mers \\ \midrule,
			table foot = \bottomrule]%
			{../tables/loci_table.csv}%
			{}%
			{\Trait & \Locus & \Gene & \Causal & \platypus & \vg & \paragraph & \kmers}

			\begin{tablenotes}
			\item[a] Platypus genotypes SNPs and indels
			\item[b] vg and Paragraph genotype SVs
			\item[c] Locus not discussed in main text. See Supplemental data for detailed results.
			\item[]- The approach detected no signal overlapping the gene.
			\item[]* The signal found at this locus overlaps the gene.
			\item[]** The region defined by the top 5\% (vg and Paragraph) or 1\% (Platypus and \textit{k}-mers) variants or \textit{k}-mers overlaps the gene.
			\item[]*** The most significantly associated marker or \textit{k}-mer is the causal variant.
			\end{tablenotes}

>>>>

			\csvreader[head to column names,
			tabular = llllccc,
			table head = \toprule Trait & Locus & Gene & Causal variant & Platypus\tnote{a} & Paragraph\tnote{b} & \textit{k}-mers \\ \midrule,
			table foot = \bottomrule]%
			{../tables/loci_table.csv}%
			{}%
			{\Trait & \Locus & \Gene & \Causal & \platypus & \paragraph & \kmers}

			\begin{tablenotes}
			\item[a] Platypus genotypes SNPs and indels
			\item[b] Paragraph genotypes SVs
			\item[c] Locus not discussed in main text. See Supplemental data for detailed results.
			\item[]- The approach detected no signal overlapping the gene.
			\item[]* The signal found at this locus overlaps the gene.
			\item[]** The region defined by the top 5\% (Paragraph) or 1\% (Platypus and \textit{k}-mers) variants or \textit{k}-mers overlaps the gene.
			\item[]*** The most significantly associated marker or \textit{k}-mer is the causal variant.
			\end{tablenotes}
